---
title: 'CSX460 Project: Kaggle Titanic'
author: "Jiangjie Man (Jack)"
date: "November 8, 2015"
output: pdf_document
---

Project Description
-----------------------------------------------------------------------------
This is the course project of **CSX460:Practical Machine Learning (with R)** 

Also, it is a Shiny Application developed using the Kaggle's Titanic dataset that predicts the survival of the passengers on the Titanic.

About the Titanic Disaster
-----------------------------------------------------------------------------
The sinking of the RMS Titanic is one of the most infamous shipwrecks in history.  On April 15, 1912, during her maiden voyage, the Titanic sank after colliding with an iceberg, killing 1502 out of 2224 passengers and crew. This sensational tragedy shocked the international community and led to better safety regulations for ships.

One of the reasons that the shipwreck led to such loss of life was that there were not enough lifeboats for the passengers and crew. Although there was some element of luck involved in surviving the sinking, some groups of people were more likely to survive than others, such as women, children, and the upper-class.

Source code and Visualization
-----------------------------------------------------------------------------
import libraries
```{r}
library(rpart)
library(caret)
library(randomForest)
library(party)
library(rpart.plot)
library(rattle)
library(ggplot2)
```

Set working directory and import datafiles to the top of the file:

```{r}
setwd("~/Desktop/Coding/Projects/Kaggle-Titanic/ShinyApp")
train <- read.csv("data/train.csv")
test <- read.csv("data/test.csv")
```

First, check dataframe and see how many people survived:

```{r}
str(train)
str(test)
table(train$Survived)
```

According to Kaggle's description, some groups of people were more likely to survive than others, such as women, children, and the upper-class. Summary and plot the gender and class to see if there are any patterns:

```{r, echo=FALSE}
GenderSurvival <- table(train$Survived, train$Sex)
PclassSurvival <- table(train$Survived, train$Pclass)
prop.table(GenderSurvival, 2)
prop.table(PclassSurvival, 2)
aggregate(Survived ~ Pclass + Sex, data = train, FUN = function(x) {sum(x)/length(x)})
barplot(GenderSurvival, xlab = "Gender", ylab = "Number of People", main = "Survival between male and female")
barplot(PclassSurvival, xlab = "Cabin Class", ylab = "Number of People", main = "Survival among different classes")
```

Then, plotting for the continuous variables:

```{r, echo=FALSE}
plot(density(train$Age, na.rm = TRUE))
plot(density(train$Fare, na.rm = TRUE))
```

Important part: Feature Engineering

```{r}
# Bind the two datasets together:
test$Survived <- NA
combi <- rbind(train, test)

# Feature engineering
combi$Name <- as.character(combi$Name)
combi$Title <- sapply(combi$Name, FUN = function(x) {strsplit(x, split = '[,.]')[[1]][2]})
combi$Title <- sub(' ', '', combi$Title)
combi$Title[combi$Title %in% c('Mme', 'Mlle')] <- 'Mlle'
combi$Title[combi$Title %in% c('Capt', 'Don', 'Major', 'Sir')] <- 'Sir'
combi$Title[combi$Title %in% c('Dona', 'Lady', 'the Countess', 'Jonkheer')] <- 'Lady'
combi$Title <- factor(combi$Title)
combi$FamilySize <- combi$SibSp + combi$Parch + 1
combi$Surname <- sapply(combi$Name, FUN = function(x) {strsplit(x, split = '[,.]')[[1]][1]})
combi$FamilyID <- paste(as.character(combi$FamilySize), combi$Surname, sep = "")
combi$FamilyID[combi$FamilySize <= 2] <- 'Small'
famIDs <- data.frame(table(combi$FamilyID))
famIDs <- famIDs[famIDs$Freq <= 2,]
combi$FamilyID[combi$FamilyID %in% famIDs$Var1] <- 'Small'
combi$FamilyID <- factor(combi$FamilyID)
```

Check to see if there are any missing values and replace it with mean:

```{r}
summary(combi)
```

```{r}
Agefit <- rpart(Age ~ Pclass + Sex + SibSp + Parch + Fare + Embarked + Title + FamilySize, data=combi[!is.na(combi$Age),], method="anova")
combi$Age[is.na(combi$Age)] <- predict(Agefit, combi[is.na(combi$Age),])
combi$Embarked <- ifelse(combi$Embarked == '', "S", combi$Embarked)
combi$Embarked <- factor(combi$Embarked)
combi$Fare <- ifelse(is.na(combi$Fare), mean(combi$Fare, na.rm = TRUE), combi$Fare)
combi$FamilyID2 <- combi$FamilyID
combi$FamilyID2 <- as.character(combi$FamilyID2)
combi$FamilyID2[combi$FamilySize <= 3] <- 'Small'
combi$FamilyID2 <- factor(combi$FamilyID2)
```

Build models (maybe a bit slow for some models):

```{r}
# partition data
train <- combi[1:891,]
test <- combi[892:1309,]

# (1) Fitting logistic regression model:
fit.lm <- glm(Survived ~ Pclass + Sex + Age + Sex * Pclass + FamilySize, family = binomial, data = train)
test$Survived <- predict(fit.lm, test, type = "response")

# (2) Fitting rpart model(decision tree):
fit.rp <- rpart(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID, data = train, method = "class")
test$Survived <- predict(fit.rp, test, type = "class")

# (3) Fitting rf model(random forest):
set.seed(123)
ctrl <- trainControl(method = "cv", number = 10, repeats = 10)
fit.rf <- train(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID2, data = train, method = "rf", trControl = ctrl)
test$Survived <- predict(fit.rf, test)

# (4) Fitting cforest model(conditional inference forest):
set.seed(123)
fit.ct <- cforest(as.factor(Survived) ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID, data = train, controls = cforest_unbiased(ntree = 3000, mtry = 3))
test$Survived <- predict(fit.ct, test, OOB = TRUE, type = "response")
```

Decision Tree Model:

```{r, echo = FALSE}
fit.rp <- rpart(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked + Title + FamilySize + FamilyID, data = train, method = "class")
fancyRpartPlot(fit.rp)
```

Save model and submit:
```{r}
submit <- data.frame(PassengerId = test$PassengerId, Survived = test$Survived)
write.csv(submit, file = "submit.csv", row.names = FALSE)
```

Other Information:
-----------------------------------------------------------------------------
- Kaggle Titanic Competition: https://www.kaggle.com/c/titanic
- CSX460 Course Github Repo: https://github.com/CSX460/CSX460


