---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}

f <- function(x) {

# my solution (robust but not efficient/vectorized):
arr <- x
for (i in 1:length(x)) {
        arr[i] <- (prod(x[-i]))
        } 
  
# class solution (computation error on elements in x = 0):
# arr <- x/prod(x)
return(arr) 
}
```
Test cases:
```{r}
f(c( 1, 5, 2, 8 ))
f(c( 1, 0, 2, 8 ))
f(c( 1, 0, 0, 1 ))
```

## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers … except for: 
   multiples of 3 = “Fizz” 
   multiples of 5 = “Buzz”. 
   multiples of 3 and 5 = “FizzBuzz”
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}

f <- function(x) {
# main problem was data types in vector changing (warnings suppressed)!
options(warn=-1)
temp <- replace(x, x %% 3 == 0 & x %% 5 == 0, 'FizzBuzz')
temp <- replace(temp, as.numeric(temp) %% 3 == 0, 'Fizz')
temp <- replace(temp, as.numeric(temp) %% 5 == 0, 'Buzz')
options(warn=0)
return(temp)
}
```

Test case:
```{r}
f(1:35)
```