---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: word_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}
f <- function(x) {
  ifelse(x!=0, prod(x)/x, prod(x)/1)
}

```

## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers … except for: 
   multiples of 3 = “Fizz” 
   multiples of 5 = “Buzz”. 
   multiples of 3 and 5 = “FizzBuzz”
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}
f <- function(x) {
  ifelse ((x/15 == floor(x/15)), print("FizzBuzz"),  
        ifelse((x/5) == floor(x/5), print ("Buzz"), 
          ifelse((x/3) == floor(x/3), print ("Fizz"), print (x))))
  
}
```
