---
title: "01-exercises"
student: "Thuyen Nguyen"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


<<<<<<< HEAD
### Solution 

```{r}

f <- function(x) {
  y<-1:length(x)
  return(prod(x) / x[y])
  # ...
  
}

=======
### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}
f <- function(x) {
  y<-1:length(x)
  prod(x) / x[y]
  # ...
  
}
>>>>>>> origin/master
```
    


## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers except for: 
   multiples of 3 replaced by "Fizz"? 
   multiples of 5 replaced by "Buzz" 
   multiples of 3 and 5 replaced by "FizzBuzz""
   
### Example

    > x <- 1:20
<<<<<<< HEAD
    > fizzbuzz(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz
    # will need to figure out how to print without quotes.  default casting as text
=======
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz

>>>>>>> origin/master

### Solution

```{r}
fizzbuzz <- function(x) {
  div3<- x %% 3 == 0
  div5<- x %% 5 == 0
  div15 <- x %% 15 == 0
  
<<<<<<< HEAD
  x[which(div3 == TRUE)] <- 'Fizz'
  x[which(div5 == TRUE)] <-'Buzz'
  x[which(div15==TRUE)] <-'FizzBuzz'
  print(x)
}
=======
  x[which(div3 == TRUE)] <- 'buzz'
  x[which(div5 == TRUE)] <-'fizz'
  x[which(div15==TRUE)] <-'fizzbuzz'
  print(x)
}

```
>>>>>>> origin/master
