---
title: "01-exercises"
author: "Dennis Raj"
date: "April 4, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Solution 

```{r}
# supplied vector
x <- c(1,5,2,8) 
# create function f that iterates over the index of length 1:length(x)
# for each element in x, save the product of all the elements of x except x to vector y 
f <- function(x){
  y <- c()
  for(i in 1:length(x)){
    y[i] <- prod(x[-i])
  }
  return(y)
}
f(x)
```
    


## Exercise 2:

Write a function f(x) to accept an integer vector, and returns a vector with those numbers except for: 
   multiples of 3 replaced by "Fizz"? 
   multiples of 5 replaced by "Buzz" 
   multiples of 3 and 5 replaced by "FizzBuzz""
   
### Solution
```{r}
#Create vector of 1 through 20
x <- c(1:20)
# Define function f as a for loop that iterates over numbers in x
# Within the function replace integers wholely divisable by 3 and 5 with Fizzbuzz,
# then replace intigers wholely divisable by 3 with Fizz and by 5 with Buzz respectively
f <- function(x){
  for (i in x){
  if ( (i%%3==0) & (i%%5==0) ) { x[i] <- "Fizzbuzz" }
  else if (i%%3==0) { x[i] <- "Fizz" }
  else if (i%%5==0) { x[i] <- "Buzz" }
}
return(x)
}
f(x)
```






 
  


