---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Solution 

```{r}

f <- function(x) {
  y<-1:length(x)
  return(prod(x) / x[y])
  # ...
  
}

```
    


## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers except for: 
   multiples of 3 replaced by "Fizz"? 
   multiples of 5 replaced by "Buzz" 
   multiples of 3 and 5 replaced by "FizzBuzz""
   
### Example

    > x <- 1:20
    > fizzbuzz(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz
    # will need to figure out how to print without quotes.  default casting as text

### Solution

```{r}
fizzbuzz <- function(x) {
  div3<- x %% 3 == 0
  div5<- x %% 5 == 0
  div15 <- x %% 15 == 0
  
  x[which(div3 == TRUE)] <- 'Fizz'
  x[which(div5 == TRUE)] <-'Buzz'
  x[which(div15==TRUE)] <-'FizzBuzz'
  print(x)
}
