---
title: "Assignment 2 CSX460 Spring 2016"
author: "Octavio Suarez Munist"
date: "April 19, 2016"
output: html_document
---



This exercise uses the **Fuel Economy** data set from the **AppliedPredicitiveModeling** package.

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
dat <-data(FuelEconomy) # Needed for aesthetics ??

```



## Exercise 1

Hint: See `?cars2010`


- After the **Fuel Economy** data is loaded, combine three data sets into one data set. (Note: The name `dat` is very often used in these situations, `data` is a reserved R word.)  

```{r}    
dat <- rbind(cars2010,cars2011,cars2012) # Define 
```


- What is a good "naive guess" of FE? Show your work

```{r}
naive_guess <- mean(dat$FE)
```


- plot FE (Fuel Econonomy) vs. EngDisp. Plot the naive guess.

```{r}
ggplot (data=dat ,aes(x=EngDispl, y=FE))+geom_point()+geom_hline(aes(yintercept=naive_guess))+ stat_smooth(method="lm", se = FALSE)  
```

- Sample 10 observations from `dat`
- Plot this data. Add a line for the naive_guess. 


```{r}

set.seed(314) 

# Sample 
samp <- dat[sample(nrow(dat), 10), ] 

# Plots 
ggplot (data=samp ,aes(x=EngDispl, y=FE))+geom_point()+geom_hline(aes(yintercept=naive_guess))+ stat_smooth(method="lm", se = FALSE) 


```


## Exercise 2:


Write a loss functions for calculating:
- Root Mean Square Error
- Mean Absolute Error
- Median Absolute Error

All functions should accept two arguments: 


```{r}

rmse <- function(y,yhat) {
  sqrt(mean((yhat-y)^2))
}

mae <- function(y, yhat) {
  mean(abs(yhat-y))
}

medae <- function(y, yhat) { 
  median(abs(yhat-y))
}

```

Use these functions to evaluate the loss/performance of:
- the naive guess



## Exercise 3: Linear Model and Model Performance 

- Use `lm` to create a linear model fitting the relationship between FE and EngDispl for the cars2010 data set


```{r}
fit.2010 <- lm(FE ~ EngDispl, data=cars2010) 
```

- Use your functions to evaluate the training error
- Use your model to:
-- predict the FE for 2011. What is the RMSE errors associated with the predictions.
-- predict the FE for 2012. What is the RMSE errors associated with the predictions.

```{r}
y.2010 <- predict(fit.2010,cars2010) 
y.2011 <- predict(fit.2010,cars2011) 
y.2012 <- predict(fit.2010,cars2012)

rmse.2010 <- rmse(cars2010$FE,y.2010)
rmse.2011 <- rmse(cars2011$FE,y.2011)
rmse.2012 <- rmse(cars2012$FE,y.2012) 

```


```{r}
# DO NOT EDIT 
rmse.2010 
rmse.2011
rmse.2012
```


## Exercise 4: 

- Model the fuel economy (`FE`) as a function of `EngDispl`, `NumCyl` and `VarValve???` using the `cars2011` data set.  
- Provide betas


```{r}
fit.dat <-lm(FE ~ EngDispl+ NumCyl + VarValveLift, data=cars2011)
betas <- coef(fit.dat)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

