---
title: "05-exercises"
author: "Your Name Here"
date: "2016-05-xx"
output: html_document
---

## Reading:
- **APM** Chapter 8.1-8.5 "Regression Trees and Rule-Based Models" (25 pages)
- **APM** Chapter 14.1-14.5 "Classification Trees and Rule-Based"  

```{r, echo=FALSE, results='hide', warning=FALSE }
packs <-  c('ggplot2', 'magrittr', 'dplyr', 'caret', 'AppliedPredictiveModeling')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

.. = NULL  # For Aesthetics

```


## Exercise 1: GermanCredit

Revisit the GermanCredit data. Use `caret` to build models of `Class` using the following techniques:

- glm
- rpart
- knn
- party::ctree
- randomForest
- A method of your choice from the Caret Model List (you will need to install any dependencies)

Save the caret objects with the names provided.

```{r}

# Your work here. 

fit.glm <- ..
fit.knn <- ..
fit.rpart <- ..
fit.rf <- ..
fit.myown <- ..


````


- Compare the models using `caret::confusionMatrix`
- Comparing the models Using the `pROC` packages
  - create ROC curves for the models 
  
Show your work! 

```{r}

.. # YOUR WORK HERE

```


Q: Which models would you select based on these tools?

Q: If you assume that a `Class=="bad""` is 10 more costly than `Class=="good"`, determine your threshold for the model of your choice.  Show your work.


```{r}

.. # YOUR WORK HERE


```
