---
title: "03-assignment: Trees"
author: "Christopher Brown"
date: "October 12, 2015"
output: html_document
---

## Readings

In Applied Predictive Modeling (APM) read:
- Chapter 8.1 - 8.8, 
- Chapter 11
- Chapter 14.1 - 14.5, 14.8

## Problems: Due October 26th, 2015 

- Project Update. (I will put a template in the projects folder for you to report your status on.) 

- Exercises, In APM: 

8.1 (a) - (C)
8.4 (a) - (b)
14.2


8.1
```{r}
library(mlbench)
set.seed(200)
simulated <- mlbench.friedman1(200, sd = 1)
simulated <- cbind(simulated$x, simulated$y)
simulated <- as.data.frame(simulated)
colnames(simulated)[ncol(simulated)] <- "y"
```

(a)
```{r}
library(randomForest)
library(caret)
model1 = randomForest(y ~ ., data = simulated, importance = TRUE, ntree = 1000)
rfImp1 = varImp(model1, scale = FALSE)

model1
rfImp1
```
No significant usage of uninformative predictors (`V6` - `V10`).

(b)
```{r}
simulated$duplicate1 = simulated$V1 + rnorm(200) * .1
cor(simulated$duplicate1, simulated$V1)

model2 = randomForest(y ~ ., data = simulated, importance = TRUE, ntree = 1000)
rfImp2 = varImp(model2, scale = FALSE)

model2
rfImp2
```
The importance score for `V1` decreases significantly when adding another predictor that is also highly correlated with `V1`.

(c)
```{r}
library(party)

set.seed(12345)
cforest1 = cforest(y ~ ., data = simulated[, 1:11], controls = cforest_control(ntree = 1000))
set.seed(12345)
cforest2 = cforest(y ~ ., data = simulated, controls = cforest_control(ntree = 1000))

cfImp1 = varimp(cforest1)
cfImp2 = varimp(cforest2)
# cfImp1con = varimp(cforest1, conditional = TRUE)
# cfImp2con = varimp(cforest2, conditional = TRUE)

cfImp1
cfImp2
# cfImp1con
# cfImp2con
```
Yes, the pattern is almost the same. Also, conditional `varimp` is too slow to compute...

8.4
```{r}
library(AppliedPredictiveModeling)
data(solubility)
```

(a)
```{r}
# solTrain = solTrainXtrans[[209]]
# solTest = solTestXtrans[[209]]
solTrain = subset(solTrainXtrans, select="MolWeight")
solTest = subset(solTestXtrans, select="MolWeight")

set.seed(12345)
rpartmodel = train(solTrain, solTrainY, method = "rpart", tuneLength = 1)
rpartmodel
rpartpred = predict(rpartmodel, solTest)
rpartTest = data.frame(Method = "rpart", Y=solTestY, X=rpartpred)
plot(rpartTest)
```

(b)
```{r}
set.seed(12345)
rfmodel = train(solTrain, solTrainY, method = "rf", tuneLength = 1)
rfmodel
rfpred = predict(rfmodel, solTest)
rfTest = data.frame(Method = "rf", Y=solTestY, X=rfpred)
plot(rfTest)
```

14.2
```{r}
library(C50)
data(churn)
```

(a)
```{r}
set.seed(12345)
rpartmodel = train(churn ~., data=churnTrain, method = "rpart", tuneLength = 10)
plot(rpartmodel)
rpartpred = predict(rpartmodel, churnTest)
table(churnTest$churn, rpartpred)
```

(b)
```{r}
#bagmodel = bag(churn ~. , data=churnTrain)
```

(c)
```{r}

```

(d)
```{r}

```