---
title: "02-exercises"
author: "Bo Wu"
date: "April 13, 2016"
output: html_document
---

This exercise uses the **Fuel Economy** data set from the **AppliedPredicitiveModeling** package.

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
... = NULL  # Needed for aesthetics 

```



## Exercise 1

Hint: See `?cars2010`


- After the **Fuel Economy** data is loaded, combine three data sets into one data set. (Note: The name `dat` is very often used in these situations, `data` is a reserved R word.)  

```{r}
dat <- bind_rows(cars2010, cars2011, cars2012)    # Define 
```


- What is a good "naive guess" of FE? Show your work

```{r}
naive_guess <- median(dat $FE)
```


- plot FE (Fuel Econonomy) vs. EngDisp. Plot the naive guess.

```{r}
# ... ggplot2  
qplot( dat$EngDispl, dat$FE)+ geom_hline(yintercept = naive_guess, color="red")
```

- Sample 10 observations from `dat`
- Plot this data. Add a line for the naive_guess. 


```{r}

set.seed(314) 

# Sample 
samp <- dat %>% sample_n(10) 

# Plots 
...
samp %>% ggplot( aes(x=EngDispl, y=FE)) + geom_point() + geom_hline(yintercept = naive_guess, color="red") + stat_smooth(method="lm", se = FALSE)

plot(samp$FE - naive_guess)
```




## Exercise 2:


Write a loss functions for calculating:
- Root Mean Square Error
- Mean Absolute Error
- Median Absolute Error

All functions should accept two arguments: 


```{r}

rmse <- function(y,yhat) {
  (y - yhat) ^ 2 %>%  mean %>% sqrt
}

mae <- function(y, yhat) {
  (y - yhat) %>%  abs %>%  mean
}

medae <- function(y, yhat) { 
  (y - yhat) %>% abs %>% median
}

```

Use these functions to evaluate the loss/performance of:
- the naive guess
RMSE = 8.108
MAE = 6.305
MEDAE = 5.4

## Exercise 3: Linear Model and Model Performance 

- Use `lm` to create a linear model fitting the relationship between FE and EngDispl for the cars2010 data set


```{r}
fit.2010 <- lm(FE ~ EngDispl, data=cars2010) 
```

- Use your functions to evaluate the training error
- Use your model to:
-- predict the FE for 2011. What is the RMSE errors associated with the predictions.
-- predict the FE for 2012. What is the RMSE errors associated with the predictions.

yhat <- predict (fit.dat, newdata=car2011)
gplot( y=cars2012$FE, x=yhat) + geom_abline(yintercept = 0, slope=1)
fit.dat %>% summary ()

```{r}

y.2010 <- predict (fit.2010, newdata=cars2011) 
y.2011 <- predict (fit.2010, newdata=cars2011) 
y.2012 <- predict (fit.2010, newdata=cars2012)

rmse.2010 <- rmse(cars2010$FE, y.2010)
rmse.2011 <- rmse(cars2011$FE, y.2011)
rmse.2012 <- rmse(cars2012$FE, y.2012) 

```


```{r}
# DO NOT EDIT 
rmse.2010 
rmse.2011
rmse.2012
```


## Exercise 4: 

- Model the fuel economy (`FE`) as a function of `EngDispl`, `NumCyl` and `VarValve` using the `cars2011` data set.  
- Provide betas


```{r}
fit.2011 <- lm(FE ~ EngDispl + NumCyl + IntakeValvePerCyl, data=cars2011)
betas <- coefficients(fit.2011)
```
