---
title: "02-exercises"
author: "Christopher Brown"
date: "April 13, 2016"
output: html_document
---

This exercise uses the **Fuel Economy** data set from the **AppliedPredicitiveModeling** package.

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
... = NULL  # Needed for aesthetics 

```


## Exercise 1

Hint: See `?cars2010`


- After the **Fuel Economy** data is loaded, combine three data sets into one data set. (Note: The name `dat` is very often used in these situations, `data` is a reserved R word.)  

```{r}
data(FuelEconomy)
dat <- bind_rows(cars2010,cars2011,cars2012) # cars2010, cars2011, cars2012)    # Define 

```

- What is a good "naive guess" of FE? Show your work

```{r}
naive_guess <- median(dat$FE)
naive_guess
qplot(dat$FE-naive_guess)
```


- plot FE (Fuel Econonomy) vs. EngDisp. Plot the naive guess.

```{r}
# ... ggplot2  
samp %>% ggplot(aes(x=EngDispl,y=FE)) + geom_point() + geom_hline(yintercept = naive_guess)
```

- Sample 10 observations from `dat`
- Plot this data. Add a line for the naive_guess. 


```{r}

set.seed(314) 

# Sample 
samp <-  dat %>%  dplyr::sample_n(10) 

# Plots 
samp %>% ggplot(aes(x=EngDispl,y=FE)) + geom_point() + geom_hline(yintercept = naive_guess)

(dat$FE -naive_guess)^2 %>% sum %>% sqrt #this is the root mean squared 308.4249

```


## Exercise 2:


Write a loss functions for calculating:
- Root Mean Square Error
- Mean Absolute Error
- Median Absolute Error

All functions should accept two arguments: 


```{r}

rmse <- function(y,yhat) {
  (y - yhat)^2 %>% mean %>% sqrt
}

mae <- function(y, yhat) {
  mean(abs(y-yhat))
}

medae <- function(y, yhat) { 
  median(abs(y-yhat))
}

```
y
yhat

Use these functions to evaluate the loss/performance of:
- the naive guess



## Exercise 3: Linear Model and Model Performance 

- Use `lm` to create a linear model fitting the relationship between FE and EngDispl for the cars2010 data set


```{r}
#fit. 2010 <- ...
fit.dat_2010 <- lm(formula = FE ~ EngDispl, data=cars2010)
fit.dat_2011 <- lm(formula = FE ~ EngDispl, data=cars2011)
fit.dat_2012 <- lm(formula = FE ~ EngDispl, data=cars2012)
#fit.dat <- lm(formula = FE ~ EngDispl+CarlineClassDesc+NumGears, data=dat)
#dat %>% select(CarlineClassDesc) %>% table
yhat_2010 = predict.lm(fit.dat_2010, newdata = cars2010)
yhat_2011 = predict.lm(fit.dat_2011, newdata = cars2011)
yhat_2012 = predict.lm(fit.dat_2012, newdata = cars2012)
qplot(y=cars2010$FE,x=yhat_2010)
qplot(y=cars2010$FE,x=yhat_2010)+geom_abline(intercept=0,slope = 1)

```

- Use your functions to evaluate the training error
- Use your model to:
-- predict the FE for 2011. What is the RMSE errors associated with the predictions.
-- predict the FE for 2012. What is the RMSE errors associated with the predictions.
dat

```{r}
y.2010 <- cars2010$FE
y.2011 <- cars2011$FE 
y.2012 <- cars2012$FE
rmse.2010 <- rmse(y.2010,yhat_2010)
rmse.2011 <- rmse(y.2011,yhat_2011)
rmse.2012 <- rmse(y.2012,yhat_2012) 
```


```{r}
# DO NOT EDIT 
rmse.2010 
rmse.2011
rmse.2012
```

## Exercise 4: 

- Model the fuel economy (`FE`) as a function of `EngDispl`, `NumCyl` and `VarValve` using the `cars2011` data set.  
- Provide betas


```{r}
fit.2011 <- lm(formula = FE ~ EngDispl+NumCyl+VarValveTiming, data=cars2011)
fit.2011
yhat_fit2011 = predict.lm(fit.2011, newdata = cars2011)
qplot(y=cars2011$FE,x=yhat_fit2011)
qplot(y=cars2011$FE,x=yhat_fit2011)+geom_abline(intercept=0,slope = 1)

betas <- c(-3.906,-1.110,3.594)

```
