---
title: "Advanced Models"
author: "Christopher Brown"
date: "October 19, 2015"
output: html_document
---


# General question

Generically and regardless of model type, what is the function of the tuning parameters?

```
```

This assignment demonstrates the use of caret for constructing models. Each model should be built and compared using using RSquared as the performance metric calculated using 10-fold repeated cross-validation with 3 folds.



```{r}
library(caret)
# library(mlbench)
data(cars, package="caret")
```


Using caret, 
fit a linear regression model? 
What is causing the warnings? What are some strategies for eliminating them?
What is the differnece in performance between the first model and the erro free model?


```{r}

```


# RPart
fit a rpart model.
How does this model compare to the 

```{r}

```


Plot the tuning parameter, C_p against the "RMSE". Orient the plot  so that models get better as you move to the left. 

```{r}
```

What does the plot tell you? 


# CTREE

Do the same for a `ctree` model.
```{r}
```

Compare the three models?

Which is best?  Why? 




# Bagging 


