---
title: "Advanced Models"
author: "Christopher Brown"
date: "October 19, 2015"
output: html_document
---


# General question

Generically and regardless of model type, what is the function of the tuning parameters?

```
Control for the bias-variance trade-off.
```

This assignment demonstrates the use of caret for constructing models. Each model should be built and compared using using RSquared as the performance metric calculated using 10-fold repeated cross-validation with 3 folds.



```{r}
library(caret)
# library(mlbench)
data(cars, package="caret")
```



```{r}
form = Price ~ . 
ctrl <- trainControl( method="repeatedcv", number=3 )
```


Using caret, 
fit a linear regression model? 
What is causing the warnings? What are some strategies for eliminating them?
What is the differnece in performance between the first model and the erro free model?


```{r}
fit.lm <- 
  train( 
    form , data = cars, method="lm"
    , metric=c("Rsquared"), trControl=ctrl 
  )
```


# RPart
fit a rpart model.
How does this model compare to the 

```{r}
s <- seq(4,7,0.25)
grid = data.frame( cp=1*10^-s)
fit.rp <- 
  train( 
    form , data = cars, method="rpart"
    , trControl=ctrl
    , tuneGrid = grid
    # , tuneLength = 10 
    , metric="Rsquared"
  )
```

Plot the tuning parameter, C_p against the "RMSE". Orient the plot  so that models get better as you move to the left. 

```{r}
fit.rp %>% plot( xTrans = function(x) -log(x), metric="RMSE" )
```

What does the plot tell you? 


# CTREE

Do the same for a `ctree` model.
```{r}
fit.ct <- train( Price ~ . , data = cars, method="ctree", metric="Rsquared" )
```

Compare the three models?

Which is better?


 


