---
title: "Advanced Models"
author: "Christopher Brown"
date: "October 19, 2015"
output: html_document
---


# General question

Generically and regardless of model type, what is the function of the tuning parameters?

```
Control for the bias-variance trade-off.
```

This assignment demonstrates the use of caret for constructing models. Each model should be built and compared using using RSquared as the performance metric calculated using 10-fold repeated cross-validation with 3 folds.



```{r}
library(caret)
# library(mlbench)
data(cars, package="caret")
```


Using caret, 
fit a linear regression model? 
```
See below
```
What is causing the warnings? What are some strategies for eliminating them?
```
prediction from a rank-deficient fit may be misleading

Drop some highly correlated predictors.
```
What is the differnece in performance between the first model and the erro free model?
```
New model is typically worse on training set and better on test set.
```


```{r warning=FALSE}
library(caTools)
set.seed(123456)
split = sample.split(cars$Price, SplitRatio = 0.7)
train = subset(cars, split==TRUE)
test = subset(cars, split==FALSE)
trc = trainControl(method = "repeatedcv", number = 10,  repeats = 3)
lmfit = train(Price ~., data=train, method="lm", metric=c("Rsquared"), trControl = trc)
#plot(lmfit)
lmfit
```


# RPart
fit a rpart model.
How does this model compare to the 

```{r warning=FALSE}
rpartfit = train(Price ~., data=train, method="rpart", metric=c("Rsquared"), preProc = c("center", "scale"), tuneLength = 10, trControl = trc)
rpartfit
```


Plot the tuning parameter, $C_p$ against the "RMSE". Orient the plot  so that models get better as you move to the left. 

```{r}
plot(rpartfit)
```

What does the plot tell you? 
```
The performance of the model is better with smaller complexity parameter $C_p$.
```


# CTREE

Do the same for a `ctree` model.
```{r warning=FALSE}
ctreefit = train(Price ~., data=train, method="ctree", metric=c("Rsquared"), preProc = c("center", "scale"), tuneLength = 10, trControl = trc)
plot(ctreefit)
ctreefit
```

Compare the three models?
```
RMSE: lm < rpart < ctree (minimum)
rpart is worse than ctree when the parameters aren't choosed appropriately.
```

Which is best?  Why? 
```
lm. Lowest RMSE.
```



# Bagging 


