---
title: "Resampling"
author: "Christopher Brown"
date: "October 5, 2015"
output: html_document
---


```{r}
set.seed(314159)
library(ggplot2)
install.packages("plyr")
library(plyr)
data(baseball, package = "plyr")
View(baseball)
hist(baseball$ab)
```


Use the `baseball` data set from the `plyr` package for the following problem.

A very simple model to predict the number of at-bats/game **each** player has per game is given by: 
 
     abpg = sum(ab)/sum(g)  # 3.10
     

- Show that this is a bad:

```{r}
attach(baseball)
library(ggplot2)

q_err <- quote(ab/g-abpg)
q_abpg <- quote(sum(ab)/sum(g))

mean( eval(q_err.baseball), na.rm = TRUE ) # -0.65
hist( eval(q_err.baseball) )

# residuals are not mean 0
```



- Create a better model using only number of games as a predictor

```{r}

any(g==0)
baseball <- baseball[g!=0]

```


- Calculate the "Apparent" *RMSE* of this model.    

```{r}



```


Using only Recreate the model, providing a new estimate for `ab/g` and the RMSE, using:
- 5-Fold CV
- Bootstrap

```{r}



```

