---
title: "Assingment NYC Flight Data"
author: "Your Name Here"
date: "October 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, `airports.csv`, `planes.csv` and `weather.csv`.  Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
library(readr)
flights <- read_csv("flights.csv")
```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
hist(flights$arr_delay, main = "Histogram of Arrival Delays", xlab = "Arrival Delays")
hist(flights$dep_delay, main = "Histogram of Departure Delays", xlab = "Departure Delays")
```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
plot(x = flights$day,
     y = flights$arr_delay,
     main = "Scatter plot of date vs. arrival delay",
     xlab = "Date (January 2013)",
     ylab = "Arrival delay")

```



## Create tables for Categorical Variables

Create a `table` of occurences of origin airports and carrier.

```{r}
table(flights$origin, flights$carrier)

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}
airports <- read_csv("airports.csv")
planes <- read_csv("planes.csv")
weather <- read_csv("weather.csv")
library(dplyr)
x <- inner_join(flights, airports, by = c("origin" = "faa"))
x <- inner_join(x, planes, by = c("tailnum" = "tailnum"))
x <- inner_join(x, weather, by = c("time_hour" = "time_hour", "origin" = "origin"))
```



