# Boston Housing

The *mlbench* package contains the data set `BostonHousing`. This data sets 

## Question 

Create a linear regression model that predicts the medium home value of the census tract as a function of the relevant predictors. Please refer to the process diagram from class. Don't forget to examine the response and predictors variable using graphical and other means.  Show your work.

This is a `rmarkdown` Document. You can use `rmarkdown` to produce a Word Doc
file, a presentation, html file, etc. Please just submit the code.

## Answer 


```{r}
library(mlbench)
library(magrittr)
library(ggplot2)
library(MASS)

data(BostonHousing)
bh=BostonHousing

# Place your code here:

bh  %>% names  %>% cat

# crim zn indus chas nox rm age dis rad tax ptratio b lstat medv


```


`medv` is the variable that you want to predict. The others are ones that you 
want.  We will call those `Xs`

```{r}
Xs <- BostonHousing %>% names %>% setdiff('medv') 
```


You should determine if any transformation of your predictors might be 
benefitial to the  model;

```{r}

# Plot each variable

for( x in Xs ) {
  ( qplot( BostonHousing[[x]]) + xlab(x) )  %>% print
  # readline( "Press [ENTER] to see next plot.")
}

```


Variable

```{r}
bh$crim %>% scale(T,T) %>% subset(,1) %>% drop %>% truehist

for( x in Xs ) {
  if( is.factor( BostonHousing[[x]])) next
  rng = range(BostonHousing[[x]] )
  ( 
      ggplot( aes(x=BostonHousing[[nm]], y=medv), data=BostonHousing) + 
      geom_point() +
      scale_x_continuous( limits=rng ) + 
      xlab(nm)
   
  
  ) %>% print
  # readline( "Press [ENTER] to see next plot.")
}

for( nm in BostonHousing %>% names %>% setdiff('medv') ) {
  ( ggplot( aes(x=nm, y=medv), data=BostonHousing) + 
    geom_point()
  ) %>% print
  readline( "Press [ENTER] to see next plot.")
}


fit <- lm( medv ~ . , data = BostonHousing)

```



```r
# STEPWISE

library(MASS)
fit.2 <- stepAIC( fit, scope=list(lower= . ~ 1, upper = . ~ .), direction="both" )

```
