---
title: "Boston Housing"
author: "John (Yang Zhou)"
date: "October 10th 2015"
output: html_document
---

# Boston Housing

The *mlbench* package contains the data set `BostonHousing`. 

Create a linear regression model that predicts the medium home value of the census tract as a function of the relevant predictors. Please refer to the process diagram from class. Don't forget to examine the response and predictors variable using graphical and other means.  Show your work.

This is a `rmarkdown` Document. You can use `rmarkdown` to produce a Word Doc
file, a presentation, html file, etc. Please just submit the code.

```{r}
library(mlbench)
library(magrittr)
library(ggplot2)
data(BostonHousing)
```


```{r}
#View the effection that a certain feature of the data using the simple linear model
model.1 <- lm( medv ~ .,data = BostonHousing )
summary (model.1)

#use the features that have the comparitively high effection
model.2 <- lm( medv ~ . -indus - age - tax -crim, data = BostonHousing )
summary(model.2)
#see the efficiency of the model by viewint the rmse 
rmse(model.1$fitted.values, BostonHousing$medv)
rmse(model.2$fitted.values, BostonHousing$medv)


## Compare Point Estimates
ggplot( aes(x=medv, y=model.1$fitted.values), data=BostonHousing ) + geom_point() +
  coord_equal( ylim=c(0,50), xlim=c(0,50) ) + 
  geom_abline( slope=1, intercept=0, color="red") +
  xlab( "BostonHousing") + 
  ylab("Estimated BostonHousing") + 
  theme( plot.background = element_blank() )

ggplot( aes(x=medv, y=model.2$fitted.values), data=BostonHousing ) + geom_point() +
  coord_equal( ylim=c(0,50), xlim=c(0,50) ) + 
  geom_abline( slope=1, intercept=0, color="red") +
  xlab( "BostonHousing") + 
  ylab("Estimated BostonHousing") + 
  theme( plot.background = element_blank() )

#compare distributions 
compare_dists <- function (...) 
{
    ll <- list(...)
    nms_1 <- names(ll)
    nms_2 <- as.character(dots(...))
    if (is.null(nms_1)) 
        nms_1 <- nms_2
    nms_1[is.na(nms_1) | nms_1 == ""] <- nms_2[is.na(nms_1) | 
        nms_1 == ""]
    names(ll) <- nms_1
    DF <- NULL
    for (nm in names(ll)) {
        df <- data.frame(dist = nm, value = ll[[nm]])
        DF <- if (is.null(DF)) 
            df
        else rbind(DF, df)
    }
    ggplot(data = DF, aes(x = value, fill = dist)) + geom_histogram() + 
        facet_grid(dist ~ .)
}

compare_dists( observed=model.1$medv, fitted=model$fitted.values ) +
  theme(legend.position = "none") +
  theme(
    # panel.background = element_blank() # element_rect(fill = "transparent",colour = NA)#, # or element_blank()
    # panel.grid.minor = element_blank(), 
    # panel.grid.major = element_blank(),
    plot.background  = element_rect(fill = "transparent",colour = NA)
  )

#step wise
library(MASS)

f <- stepAIC( model.1, scope=list(lower=FE~1, upper=FE~.), direction="backward" ) 
```












