---
title: "Assingment NYC Flight Data - Answer"
author: "Christopher Brown"
date: "October 5, 2016"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(magrittr)
library(lubridate)
library(stringr)
library(dplyr)
library(data.table)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling by 
joining/merging flight data. In the folder `02-fundamentals/data` there are four 
CSV files: `flights.csv`, `airports.csv`, `planes.csv` and `weather.csv`.  
Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
# data.frame / dplyr
flights  <- "data/flights.csv" %>% read_csv 
# flights <- "data/flights.csv" %>% read.csv(stringsAsFactors=FALSE)
planes   <- read_csv("data/planes.csv")
airports <- read_csv("data/airports.csv") 
weather  <- read_csv("data/weather.csv")

# data.tables
flightsDT  <- fread("data/flights.csv") 
planesDT   <- fread("data/planes.csv")  %>% setkey(tailnum)
airportsDT <- fread("data/airports.csv")  %>% setkey(faa) 
weatherDT  <- fread("data/weather.csv") %>%   setkey(origin,year,month,day,hour)

```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
( flights$dep_delay %>% qplot )   # OR 

ggplot( data=flights, aes(x=arr_delay)) + geom_histogram() + scale_x_log10()

ggplot( data=flights, aes(x=arr_delay)) + geom_histogram() + scale_x_sqrt()

```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

First create a date variable from year/month/day:

```{r}

str_pad4 <- . %>% str_pad(4,'left',0)
str_pad2 <- . %>% str_pad(2,'left',0)

ymd_hm <- function(year, month, day, hour, minute ) { 
  dates <- paste0(
    year %>% str_pad4, 
    month %>% str_pad2,
    day %>% str_pad2,
    " ",
    hour %>% str_pad2,
    ":",
    minute %>% str_pad2
  ) 
  
  dates %>% lubridate:::ymd_hm(.)
  
}

ymd <- function(year, month, day ) { 
  dates <- paste0(
    year %>% str_pad4, 
    month %>% str_pad2,
    day %>% str_pad2,
  ) 
  
  dates %>% lubridate:::ymd(.)
  
}    
  

# data.frame
  flights$dt <- 
    ymd_hm( flights$year, flights$month, flights$day, flights$hour, flights$minute ) 

# dplyr
  flights <- flights %>% mutate( dt = ymd_hm(year,month,day,hour,minute) )
 
# data.table 
  flightsDT[ , dt := ymd_hm(year,month,day,hour,minute) ] 


# Sample  
ggplot( data=flights %>% sample_n(1e3), aes(x=dt, y=arr_delay) ) +
  geom_point() + geom_smooth()


 
```



## Create tables for Categorical Variables

Create a `table` of occurences of origin airports and carrier.

```{r}

flights$carrier %>% table( useNA="always") %>% sort 
flights$origin %>% table( useNA="always") %>% sort 

table( flights$carrier, flights$origin)

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}

# merge.data.frame

## flights 
YX <- flights 

## planes
YX <- merge( YX, planes, by="tailnum", all.x = TRUE )

## airports  
YX <- merge(YX, airports, by.x="origin", by.y="faa", all.x=TRUE, suffixes=c("", ".origin")  )
YX <- merge(YX, airports, by.x="dest", by.y="faa", all.x=TRUE, suffixes=c("", ".dest")  )

## weather
# weather$date <- ymd(weather$year, weather$month, weather$day)
YX <- 
  merge( flights, weather, by=c("origin","year","month","day","hour"), all.x=TRUE, suffixes=c('',".weather") )



# data.frame

# dplyr
YX <- 
  flights %>% 
  left_join(weather, by=c("origin","year","month","day","hour") ) %>%
  left_join(planes, by='tailnum', suffixes=c('','.pl') ) %>% 
  left_join(airports, by=c('origin'='faa') ) %>% 
  left_join(airports, by=c('dest'='faa') )    

prefix_names <- function(x,prefix) { 
  setnames(x, names(x), paste0(prefix,names(x))) 
  return(invisible(x)) 
}

# data.table
YX <- flightsDT %>% copy %>% prefix_names('fl.') 
YX <- planesDT %>% copy %>% prefix_names('pl.') %>% .[ YX %>% setkey(fl.tailnum) ]
YX <- weatherDT %>% copy %>% prefix_names('we.') %>% .[ YX %>% setkeyv(c("fl.origin","fl.year","fl.month","fl.day","fl.hour")) ]
YX <- airportsDT %>% copy %>% prefix_names('orig.') %>% .[ YX %>% setkey(we.origin)  ]
YX <- airportsDT %>% copy %>% prefix_names('dest.') %>% .[ YX %>% setkey(fl.dest) ]

# BEST:
YX <- flightsDT 
YX %<>% merge( planesDT, all.x = TRUE, by='tailnum', suffixes=c('','.pl') )
YX %<>% merge( weatherDT, all.x = TRUE, by=c('origin','year','month','day','hour'), suffixes=c('','.we') )
YX %<>% merge( airportsDT, all.x = TRUE, by.x='origin', by.y='faa', suffixes=c('','.orig') )
YX %<>% merge( airportsDT, all.x = TRUE, by.x='dest', by.y='faa', suffixes=c('','.dest') )



```



