---
title: "Assingment NYC Flight Data"
author: "Your Name Here"
date: "October 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. 
In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, 
`airports.csv`, `planes.csv` and `weather.csv`.  Join/merge these tables such 
that there is one rectangular table with one row for each flight. 


Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}


```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}

```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}

```



## Create tables for Categorical Variables

Create a `table`, counting the flights by origin airports and carrier.

```{r}


```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}

```



