---
title: "Assingment NYC Flight Data"
author: "Thuyen Nguyen"
date: "April 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. 
In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, 
`airports.csv`, `planes.csv` and `weather.csv`.  Join/merge these tables such 
that there is one rectangular table with one row for each flight. 


Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
library(readr)
library(data.table)
airports <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/airports.csv") %>% setDT
flights <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/flights.csv") %>% setDT
planes <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/planes.csv") %>% setDT
weather <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/weather.csv") %>% setDT
##View(airports)
##View(weather)


```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
##removing NA from data set
dep_delay <- na.omit(flights$dep_delay) 

hist(dep_delay,breaks=100,xlim=c(-50,500),xlab="departure delay",main="histogram of departure delay")
## to see the impact of the long tail
hist(dep_delay,breaks=100,xlim=c(-50,500),xlab="departure delay",main="histogram of departure delay",ylim=c(0,200))

##removing NA from data set
arr_delay <- na.omit(flights$arr_delay) 

hist(arr_delay,breaks=100,xlim=c(-100,500),xlab="arrival delay",main="histogram of arrival delay")
## to see the impact of the long tail
hist(arr_delay,breaks=100,xlab="arrival delay",main="histogram of arrival delay",ylim=c(0,400))

```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
library(ggplot2)
library(lubridate)
flights$date <- as.Date(with(flights, paste(year, month, day,sep="-")), "%Y-%m-%d")
ggplot(flights, aes(flights$date, arr_delay)) +geom_point()
```



## Create tables for Categorical Variables

Create a `table`, counting the flights by origin airports and carrier.

```{r}
flight_origin <- flights %>% group_by(origin, carrier) %>% summarize(total.count=n())
View(flight_origin)

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}
library(margrittr)
library(dtplyr)

data_join <- flights %>%
  transform(dephour = floor(dep_time / 100)) %>%
  inner_join(.,planes, by=c("tailnum" = "tailnum")) %>% 
  inner_join(.,airports,by=c("origin"="faa"))  %>%
  inner_join(.,airports,by=c("dest"="faa")) %>%
  inner_join(.,weather, by=c("origin"="origin","dephour"="hour","year.x"="year","month"="month","day"="day")) 

```



