---
title: "Creating  a model package"
author: "Christopher Brown"
date: "May 25, 2016"
output: html_document
---

```{r,echo=FALSE, warning=FALSE, results='hide', message=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr', 'caret')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
.. = NULL  # Needed for aesthetics 

FE <- dplyr::bind_rows(cars2010, cars2011, cars2012)    # Define Da

```


Model packages should contain and make available:

 * a model object named `fit` or fitting function, typically the result of the the training function, often `caret::train`.

* an optional function, `featurize` for transforming feature vectors

* a function for 



## Step 0: Train Model

```{r}

fit <- 
  train( FE ~ poly(NumCyl,2) + poly(NumGears,2) + poly(EngDispl,2), FE, method="lm" )

```


## Step 1: Create a R package


```{r, eval=FALSE}
library(devtools)
PATH = '/Temp'
dir <- file.path( PATH, 'FE.model' ) 
print(dir)
devtools::create(dir, rstudio = FALSE) 
```


## Step 2: Save the model to package

Save `fit`
* Save `fit` and `featurize` to the `data` directory; 


```{r, eval=FALSE}
DATAPATH =file.path( dir, 'data' )
dir.create( DATAPATH, showWarnings = FALSE, recursive = TRUE )
save( fit, file=file.path( dir, 'data', 'fit.rda') )
```


## Step 3: Test 

```{r, eval=FALSE}
rm(fit)
load_all(dir)
fit
predict(fit, fit$trainingData)
```

## Step 4: Createa/Update documentation

* ROxygen Documentation: `R/fit.R`, `R/featurize.R`

```
#' @name fit
#' @description model for fitting Fuel Economy based on 
#' @details ...
#' @docType data
#' @import caret randomForest etc.

NULL
```

### DESCRIPTION

Update your descriptions 

 * Author: 
 * Date:
 * **Version:**
 * LazyData: TRUE
 * Imports: caret, ...
 * etc.

  Use Sementic Versioning X.Y.Z.a 


## Step 5: Update git, add, commmit + tag changes    

```
git add ...
git commit
git tag vX.Y.Z.a
git push ...
```

## Step 6: Build Your Package

```{r, eval=FALSE}
devtools::build(dir)
```

### Step 7: Distribute your package

Warning: Dependencies may change. To ensure that everything works consider creating a packrat project or deploying using a strictly controlled environment, such as a virtual machine
