---
title: "05-exercises"
author: "Bo Wu"
date: "2016-05-17"
output: html_document
---

## Reading:
- **APM** Chapter 8.6 and 8.8 
- **APM** Chapter 14.8 
- **APM** Chapter 7.1 & 7.3 "Non-Linear Regression Models"
- **APM** Chapter 13.2 & 13.4 "Non-Linear Classifcation Models"


```{r,echo=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)
.. = NULL  # Needed for aesthetics 

FE <- dplyr::bind_rows(cars2010, cars2011, cars2012)    # Define Da

```

## Fuel Economy 


This week we return to the Fuel Economy Data having learned much about model building. This assignment is to go through the process of building several regression models and pick the most predictive model. Use the `FE` data set created for you above.


Start by making choosing a metric and making a naive guess of model performance: 

Metric: Mean
Naive Guess: 34.6
Expected Model Performance (based on Naive Guess): error = 8.108

Show your work below for the calculations

```{r} 

  
naive_guess = median(dat $FE)

#RMSE
err_naive_guess = (dat$FE - naive_guess) ^ 2 %>%  mean %>% sqrt

```


Based only your intuition, how low do your think you can get your metric: RMSE of around 2 would be acceptable.


## Examine your data

 * Plot your response/outcome 

 * Make a guess of a strong predictor: Engine Displacement 
 * Plot your response vs your predictor. 

```{r}

qplot(FE$FE)

qplot(FE$EngDispl)

qplot(FE$EngDispl, FE$FE)

```


## Build Simple Models

Using **caret**, build a simple linear model and a simple tree model. 

```{r}

ctrl <- trainControl(method="boot", number=5, classProb=TRUE, savePrediction=TRUE )

fit.lm <- train(FE ~ EngDispl, data=FE, trControl=ctrl, method ="glm")
  
fit.rp <- train(FE ~ EngDispl, data=FE, trControl=ctrl, method="rpart")

```


What did you learn about the data from these models.
The RMSE decreased signficantly from using these models. This tells me that using engine displacement indeed is a good predictor.


## Build More Advanced Models

Now refine your models. Use **caret** to build advanced models:
- one that uses model averaging (bagging) 
- one that uses boosting 

```{r}

# Your work here.
fit.bag   <- train(FE ~ EngDispl, data=FE, trControl=ctrl, method="treebag")

fit.boost <- train(FE ~ EngDispl, data=FE, trControl=ctrl, method="glmboost", metric = 'RMSE')

```


## Conclusion 

Which model would you use and why?  Under different circumstances why would you choose one of the other models.

I would used the bagged model because it reported the lowest RMSE. If you have access to a machine with enough processing power, low computing cost, and good-sized dataset, then you should use bagged and boosting models. Otherwise, you should use the simpler models. 




