---
title: "03-exercises"
author: "Your Name Here"
date: "April 20, 2016"
output: html_document
---

## Readings

***APM***

- Chapter 4 "Over Fitting and Model Tuning"
- Chapter 12.2 "Logisitic Regression""


## Miscellaneous

I am still struggling with names ...

- Please send me your picture


## Assignment 

Note: The following will set-up your environment for this exercise. If you get an error stating that the packages have not been found, you need to install those packages.


```{r,echo=FALSE, warning=FALSE, message=FALSE}

packs <-  c('AppliedPredictiveModeling', 'ggplot2', 'magrittr', 'dplyr', 'caret')

for( nm in packs ) { 
  # message(nm)
  if( ! nm  %in% installed.packages()[,1]  ) install.packages(nm)
  library(nm, character.only = TRUE)
}

# Load data set into environment
data(FuelEconomy)     # See ?cars2010
fe <- dplyr::bind_rows(cars2010, cars2011, cars2012)    # Define Da


data("GermanCredit")  # see GermanCredit

... = NULL  # Needed for aesthetics 

```


## StepAIC


Using Fuel Economy data set from the **AppliedPredictiveModeling** Package.
- fit the simplest possible model using lm
- Use MASS::StepAIC to improve the model using forward stepwise regression
- Fit the "full" model using lm
- USe MASS::StepAIC to improve the model using backward stepwise regression 

```{r}
 # Your work here
fit.simp <- lm( EngDispl ~ FE, data=fe) #simplest possible model using lm
plot(fit.simp)
summary (fit.simp)
frwdstep.reg <- stepAIC(fit.simp, direction=c("forward"))
plot(frwdstep.reg)
fit.full <- lm( EngDispl ~ ., data=fe) #full model using lm
summary (fit.full)
plot (fit.full)

```

- Are they the same model? If not why?  Which is better?


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`


```{r}

logistic <- function(x) { 
  ... # Your work here

#x <- c( -Inf:Inf )
x <- c(-10:10)
yintercept = 1
slope = 0
y <- 1 / (1 + exp((slope + yintercept*x)))

#curve(qlogis(x),-10,10)
#curve(dlogis(x),-10,10)
#curve(logit(x))
#plot(qnorm) #same as curve(logit(x))
#plot(qlogis) #y at -4,+4
}

qplot(x,y )


logistic_inv <- function(y) { 
  ... # Your work
x <- c(-10:10)
yintercept = 1
slope = 0
y <- exp((slope + yintercept*x)) / (1 + exp((slope + yintercept*x)))

}

qplot(x,y) 

```

**NOTE"** These functions are quite handy, in evaluating logistic regression results. You may want to save these functions in your own package.  

```{r}
# DO NOT EDIT
c(-Inf,0,Inf) %>% logistic

c(0,0.5,1) %>% logistic_inv

```


## German Credit Model

Using the GermanCredit data from the **Caret** package/ UCI Machine Learning Library, create a model for `Class` ("Good" vs. "Bad" ). Show your model performance.  

```{r}
library (magrittr)
library (MASS)
data(german_credit)
gm <- tbl_df(german_credit)
gm
as.data.frame(gm)
data(GermanCredit)
lm(~ ., data=GermanCredit) # place data frame in table
#find most significant predictors to use for model
#summary(german_credit)
#gm %>% data(german_credit)
dat.train <- dplyr::sample_n(data(gm), 500) #Randomly sample of 500 rows from german_credit
dat.test <- dplyr::sample_n(data(gm), 500) #Randomly sample of 500 rows from german_credit
lm( Class ~ Amount, data=GermanCredit ) #produce a linear regression

#Build model using Resampling via caret package

#Build model using Resampling via caret package knn3 to assess proportions of neighbors


```



## Iterative Correlated Feature Removal 

- Implement Kuhn's iterative feature removal function described in **APM** Section 3.5, page 47



## Synthetic Data (Optional)

Sometimes it is useful to "synthesize" feature data for to understand how a certain model behaves. 
Sythesize the following features 1000-element vectors: 

- x1: a normally distributed variable with `mean = 20` and standard deviation = 20 (`sd=8`).
- x2: a log-normally distributed feature with `meanlog = 1`, `sdlog=1.2`
- x3: a uniformly distributed feature with `min=0` and `max=50`. 

```{r}
nsamples = 20

x1 <- rnorm(nsamples,20,20)  
x2 <- rlnorm(nsamples, meanlog=1, sdlog = 1.2)
x3 <- runif(nsamples,0,50)

```

Next synthesis a response, `y` using the betas provided and an intercept that is normally distributed at 20 with standard deviation of 2. (**Hint:**  The betas thought of can be a vector or matrix)



```{r}

beta0 <- rnorm(nsamples,0,15)  # intercept!
beta1 <- 2.3
beta2 <- 4
beta3 <- 7

betas <- matrix( c(2.5, 4, 7), nrow=1  )  # 1x4 matrix

# x0 <- rep(1,nsamples) 

X  <- cbind(x1,x2,x3)  # 1000x4

y <- betas %*% t(X) %>% t
y <- y + beta0

qplot(y)
dat <- data.frame(y,X)

fit <- lm( y ~ . , dat )

coef(fit)

fit
```

- Did you recover the betas? 
- Is the model good?
- What happens if increase the value of `nsamples`? Decrease it?
- What transformations would you apply to x1? x2? x3? 

