---
title: "Caret / Recursive Partitioning"
author: "Thuyen Nguyen"
date: "May 15, 2017"
output:
  html_document: default
---

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
library(dplyr)
library(pROC)
library(partykit)
library(readr)
library(ggplot2)
library(magrittr)
library(data.table)

# .. Additional libraries
```


## Exercise 1: caret/logistic regression (5 points)

Rebuild your logistic regression model from the previous week, this time using the `caret` package. 

- Calculate the training or apparent performance of the model. 
- Calculate an unbiased measure of performance 
- Create a ROC Curve for your model

Show all work.

```{r logistic model}
# Your Work Here

#loaddata

airports <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/airports.csv") %>% setDT
flights <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/flights.csv") %>% setDT
planes <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/planes.csv") %>% setDT
weather <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/weather.csv") %>% setDT

data_join <- flights %>%
  transform(dephour = floor(dep_time / 100)) %>%
  left_join(.,planes, by=c("tailnum" = "tailnum")) %>% 
  left_join(.,airports,by=c("origin"="faa"))  %>%
  left_join(.,airports,by=c("dest"="faa")) %>%
  left_join(.,weather, by=c("origin"="origin","dephour"="hour","year.x"="year","month"="month","day"="day")) 
head(data_join)
#isolate just the lateflight
data_join$lateflight <- factor(data_join$arr_delay >= 20) 
#data_join$lateflight %>% qplot

#remove NA data
data_join <- na.omit(data_join [,c("lateflight","dep_delay","month","air_time","distance","carrier","lat.y","lon.y","arr_delay")])

#create training data
set.seed(1234)
inTraining <- createDataPartition(data_join$lateflight, p=0.75,list=FALSE)

#Train the model using caret

train <- trainControl(method = "cv", number = 20)
training <- data_join[inTraining,]
testing <- data_join[-inTraining,]

fitformula <- lateflight ~ dep_delay + month + air_time + distance + carrier + lat.y + lon.y
fitmodel <- train(fitformula, data = training, trControl = train, method = "glm")
 predictions <- predict(fitmodel, testing)
 confusionMatrix(predictions,testing$lateflight)
 
 fitLinear <- arr_delay ~ dep_delay + month + air_time + distance + carrier + lat.y + lon.y
 LinearModel <- train(fitLinear, data = training, trControl = train, method = "glm")
 predictLinear <- predict(LinearModel, testing)
 plot(roc(testing$lateflight,predictLinear))
 

 
```


## Exercise 2: caret/rpart (5 points)

Using the `caret` and `rpart` packages, create a **classification** model for flight delays using your NYC FLight data. Your solution should include:

- The use of `caret` and `rpart` to train a model.
- An articulation of the the problem your are 
- An naive model
- An unbiased calculation of the performance metric
- A plot of your model -- (the actual tree; there are several ways to do this)
- A discussion of your model 



Show and describe all work

```{r rpart model}
# Your Work Here

#Naive Model, randome number

set.seed(1234)
y <- sample(c(TRUE,FALSE),length(training$lateflight), TRUE)
confusionMatrix(y, data_join$lateflight)

#unbiased calculation 

formula <- lateflight ~ dep_delay + month + air_time + distance + carrier + lat.y + lon.y
model <- train(formula, data = training, trControl = train, method = "rpart")
 unBiased <- predict(model, testing)
 confusionMatrix(unBiased,testing$lateflight)

#training the model
 
TuneModel <- rpart(lateflight ~ dep_delay + month.flight + air_time + distance + carrier + lat.y + lon.y,
                   data = training,
                   method = "class",
                   control = list(cp = 0.01, minsplit = 5, maxdepth = 20))
TrainPrediction <- predict(TuneModel, testing)
confusionMatrix(TrainPrediction, testing$lateflight)

#plot the model

rpartTree <- as.party(TuneModel)
plot(rpartTree)

```


### Questions:

- Discuss the difference between the models and why you would use one model over the other?
- How might you produce an ROC type curve for the *rpart* model? 