---
title: "Caret / Recursive Partitioning"
author: "Your Name Here"
date: "Today's Date"
output: pdf_document
---

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
# .. Additional libraries
```


## Exercise 1: caret/logistic regression (5 points)

Rebuild your logistic regression model from the previous week, this time using the `caret` package. 

- Calculate the training or apparent performance of the model. 
- Calculate an unbiased measure of performance 
- Create a ROC Curve for your model

Show all work.

```{r logistic model}
# Your Work Here
```


## Exercise 2: caret/rpart (5 points)

Using the `caret` and `rpart` packages, create a **classification** model for flight delays using your NYC FLight data. Your solution should include:

- The use of `caret` and `rpart` to train a model.
- An articulation of the the problem your are 
- An naive model
- An unbiased calculation of the performance metric
- A plot of your model -- (the actual tree; there are several ways to do this)
- A discussion of your model 



Show and describe all work

```{r rpart model}
# Your Work Here
```


### Questions:

- Discuss the difference between the models and why you would use one model over the other?
- How might you produce an ROC type curve for the *rpart* model? 
