---
title: "NYCFlights: Arrival Delay Regression Model (Open Ended Variation)"
author: "Thuyen Nguyen"
date: "04/17/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NYCFlights Model

Using the rectangular data that you created last week create a model for `arr_delay`. Follow a well defined process for creating a model as discussed in class or from one of the readings. 

Break the process down into steps and create a codeblock for each step. 
 - Use as many steps you feel as necessary
 - Concisely explain each step 
 - Show all work
 
(You can start with the data that you created last week.)


## Setup Data 



```{r}
library(readr)
library(data.table)
library(dplyr)
library(ggplot2)
library(lubridate)
library(magrittr)

airports <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/airports.csv") %>% setDT
flights <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/flights.csv") %>% setDT
planes <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/planes.csv") %>% setDT
weather <- read_csv("~/Documents/CSX460/02-building-blocks/02-exercise-nycflights/data/weather.csv") %>% setDT

data_join <- flights %>%
  transform(dephour = floor(dep_time / 100)) %>%
  left_join(.,planes, by=c("tailnum" = "tailnum")) %>% 
  left_join(.,airports,by=c("origin"="faa"))  %>%
  left_join(.,airports,by=c("dest"="faa")) %>%
  left_join(.,weather, by=c("origin"="origin","dephour"="hour","year.x"="year","month"="month","day"="day")) 
head(data_join)


```
## Step 1
```{r "Step 1: [test model with a few variables that are known to cause arrival delay" }

fit <- lm(formula= arr_delay ~ +dep_delay +carrier, data=data_join)
summary(fit)
ggplot(flights, aes(dep_delay, arr_delay)) +geom_point()
```

## Step 2: ...
```{r "Step 2: [test model with other variables & lots of variables to determine significance" }

fit <- lm(formula= arr_delay ~ +carrier +flight +time_hour.x +model + engines +origin +dest, data=data_join)
summary(fit)

fit <- lm(formula= arr_delay ~ +sched_dep_time +dep_time +dep_delay +carrier +flight +time_hour.x +model + engines +origin +dest, data=data_join)

summary(fit)

```
# Question:

Is this a good model?  (Write your answer here.)

The first model is a good model with an adjusted R-Square = 0.84, only 16% of the error are not answered by the model. Dep_delay by itself has an R-Square of 0.83.  The other two variables gets us another 1 pct in R-Square.  The included scatter plot demonstrates a clear linear relationship between dep_delay and arr_delay.  There is a little bit of a fat tail effect on the left indicates that a few-minute delays can be made up during flights.  

The rest of the regression runs yielded very small adjusted R-Square. This is an indication that these coefficients are not sigificant factors for arr_delay.  The last model with a lot more variables has a higher R-Square value, but it has a lot of insigificant coefficients which will create a lot of noise and not a good model.  
